---
title: Scatterplots
author: Katherine Schneider
date: '2017-09-28'
slug: scatterplots
categories:
  - R
tags:
  - R Markdown
---
These are the pakages we will need to make the intended scatterplot;


```{r warning=FALSE,message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Scatterplots were introduced today. The lesson was started with the task of finding all homeruns and strikeouts in the MBL, then narrowing it down to the best homerun records for each player (a sum of 400 or more). This is the extracted data wanted on the scatterplot;

```{r}
query<-"SELECT playerID,sum(HR) AS career_HR,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"

result<-sqldf(query)
```

In order to visualize this into an easy-to-read scatter plot we ran the following;

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR),size=3,color="blue")+
  ggtitle("Career Strikeouts VS Homeruns for Great Hitters")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")

```

